---
title: "488_PA_Proj"
author: "Lia Amelia"
date: "September 21, 2015"
output: pdf_document
---

1. Page 126, no 15
(a) 
```{r}
library(MASS)
#SLR crim(y) & zn(x)
summary(lm.crimzn <- lm(crim~zn,Boston))
plot(lm.crimzn)
#SLR crim(y) & indus(x)
summary(lm.crimind <- lm(crim~indus,Boston))
plot(lm.crimind)
#SLR crim(y) & nox(x)
summary(lm.crimnox <- lm(crim~nox,Boston))
plot(lm.crimnox)
#SLR crim(y) & rm(x)
summary(lm.crimrm <- lm(crim~rm,Boston))
plot(lm.crimrm)
#SLR crim(y) & age(x)
summary(lm.crimage <- lm(crim~age,Boston))
plot(lm.crimage)
#SLR crim(y) & dis(x)
summary(lm.crimdis <- lm(crim~dis,Boston))
plot(lm.crimdis)
#SLR crim(y) & rad(x)
summary(lm.crimrad <- lm(crim~rad,Boston))
plot(lm.crimrad)
#SLR crim(y) & tax(x)
summary(lm.crimtax <- lm(crim~tax,Boston))
plot(lm.crimtax)
#SLR crim(y) & ptratio(x)
summary(lm.crimpt <- lm(crim~ptratio,Boston))
plot(lm.crimpt)
#SLR crim(y) & black(x)
summary(lm.crimbla <- lm(crim~black,Boston))
plot(lm.crimbla)
#SLR crim(y) & lstat(x)
summary(lm.crimls <- lm(crim~lstat,Boston))
plot(lm.crimls)
#SLR crim(y) & medv(x)
summary(lm.crimmedv <- lm(crim~medv,Boston))
plot(lm.crimmedv)
#SLR crim(y) & chas(x)
#factor variable chas
Boston$chas <- factor(Boston$chas)
summary(Boston$chas)
levels(Boston$chas) <- c(0,1)
summary(lm.crimchas <- lm(crim~chas,Boston))
plot(lm.crimchas)
```
Simple linear regression models for every predictors show there is association between predictors and crime rate by town except for predictor $chas$, which p-value is higher than 0.05. 

(b)
```{r}
#multiple regression model
summary(lm.crim <- lm(crim~zn+indus+chas+nox+rm+age+dis+rad+tax+ptratio+black+lstat+medv, Boston))
```
The result of multiple regression model is different with simple linear regression model for each predictors. Some predictors that are significant for simple linear regression model appear to be not significant in multiple regression model. Predictors that are significantly different from 0 for multiple regression model with ${\alpha}=0.05$ are $zn$, $dis$, $rad$, $black$, and $medv$. 

(c)
```{r}
#print all slope of every SLR model
x_crime <- c(lm.crimzn$coefficients[2],
             lm.crimind$coefficients[2],
             lm.crimchas$coefficients[2], 
             lm.crimnox$coefficients[2],     
             lm.crimrm$coefficients[2], 
             lm.crimage$coefficients[2], 
             lm.crimdis$coefficients[2], 
             lm.crimrad$coefficients[2], 
             lm.crimtax$coefficients[2], 
             lm.crimpt$coefficients[2], 
             lm.crimbla$coefficients[2], 
             lm.crimls$coefficients[2], 
             lm.crimmedv$coefficients[2])

#print all slopes from multiple regression model
y_crime <- lm.crim$coefficients[2:14]

#create data fram for x_crime and y_crime
xy_crime <- data.frame(x_crime, y_crime)

#plot x_crime and y_crime
plot(xy_crime)

```

(d)
```{r}
#nonlinear crim(y) & zn(x)
summary(lm.noncrimzn <- lm(crim~poly(zn,3),Boston))
#nonlinear crim(y) & indus(x)
summary(lm.noncrimind <- lm(crim~poly(indus,3),Boston))
#nonlinear crim(y) & nox(x)
summary(lm.noncrimnox <- lm(crim~poly(nox,3),Boston))
#nonlinear crim(y) & rm(x)
summary(lm.noncrimrm <- lm(crim~poly(rm,3),Boston))
#nonlinear crim(y) & age(x)
summary(lm.noncrimage <- lm(crim~poly(age,3),Boston))
#nonlinear crim(y) & dis(x)
summary(lm.noncrimdis <- lm(crim~poly(dis,3),Boston))
#nonlinear crim(y) & rad(x)
summary(lm.noncrimrad <- lm(crim~poly(rad,3),Boston))
#nonlinear crim(y) & tax(x)
summary(lm.noncrimtax <- lm(crim~poly(tax,3),Boston))
#nonlinear crim(y) & ptratio(x)
summary(lm.noncrimpt <- lm(crim~poly(ptratio,3),Boston))
#nonlinear crim(y) & black(x)
summary(lm.noncrimbla <- lm(crim~poly(black,3),Boston))
#nonlinear crim(y) & lstat(x)
summary(lm.noncrimls <- lm(crim~poly(lstat,3),Boston))
#nonlinear crim(y) & medv(x)
summary(lm.noncrimmedv <- lm(crim~poly(medv,3),Boston))
#nonlinear crim(y) & chas(x)
#Boston$chas <- factor(Boston$chas)
#summary(Boston$chas)
#levels(Boston$chas) <- c(0,1)
#summary(lm.noncrimchas <- lm(crim~poly(chas,3),Boston))
```

2. 173
```{r}
#Logistic regression
medianC <- median(Boston$crim) #calculate median
Boston["medC"] <- NA #create empty column of medC
Boston$medC <- as.numeric(Boston$crim > medianC) #group crime rate

#create subset train & test
set.seed(12345)
random <- sample(1:506, 506, replace = FALSE)
train <- random[1:253]
test <- random[254:506]
Boston.train <- Boston[train,]
Boston.test <- Boston[test,]

#create a model using train data with logit
glm.med <- glm(medC~zn+indus+nox+rm+dis+rad+
          tax+ptratio+black+lstat+medv, Boston,family=binomial, subset=train)

#apply the model from data train to data test
glm.probs <- predict(glm.med,Boston.test,type="response")

#checking match and mismatch
glm.pred <- rep(0,253) #create an array of 253 with all 0 in it
glm.pred[glm.probs > 0.5]=1
table(glm.pred,Boston.test$medC)
mean(glm.pred==Boston.test$medC) #match
mean(glm.pred!=Boston.test$medC) #mismatch

#check which factors are significant
glm.med1 <- glm(medC~zn+indus+nox+rm+dis+rad+tax+
            ptratio+black+lstat+medv, Boston,family=binomial)
summary(glm.med1)
#generate model with only significant predictors
glm.med2 <- glm(medC~zn+nox+dis+rad+tax+ptratio+black+lstat, Boston,family=binomial,subset=train)
glm.probs2 <- predict(glm.med2,Boston.test,type="response")
glm.pred2 <- rep(0,253)
glm.pred2[glm.probs2 > 0.5]=1
table(glm.pred2,Boston.test$medC)
mean(glm.pred2==Boston.test$medC)
mean(glm.pred2!=Boston.test$medC)

#LDA
library(MASS)
#run lda model using train data
lda.med <- lda(medC~zn+indus+nox+rm+dis+rad+tax+ptratio+
black+lstat+medv, Boston,subset=train)
lda.med
#applying model generated with train data to test data
#predict function returns a list of 3(class, posterior,and x)
lda.pred <- predict(lda.med,Boston.test)
names(lda.pred)
lda.class <-lda.pred$class
#compare number of 0 and 1 b/w prediction with the actual test data
table(lda.class,Boston.test$medC)
#calc the mean of matching 0 or 1 b/w prediction w/ test data
mean(lda.class==Boston.test$medC)
mean(lda.class!=Boston.test$medC)

#we can try with another predictor, instead of using all predictors 
#we can try to use some predictors only

#KNN
library(class)
#create matrix combination of all predictors for train & test data
attach(Boston)
train.X <- cbind(zn,indus,nox,rm,dis,rad,tax,ptratio,black,lstat,
                 medv)[train,]
test.X <- cbind(zn,indus,nox,rm,dis,rad,tax,ptratio,black,lstat,
                medv)[test,]
train.medC <- medC[train]
set.seed(1)
knn.pred <- knn(train.X,test.X,train.medC,k=1)
table(knn.pred,Boston.test$medC)
mean(knn.pred==Boston.test$medC)
```



